---
title: "Skill-building in an upper-level biology CURE"
author: "Abby Beatty"
date: "December 04, 2020"
output:
  pdf_document: default
  html_document: default
---

#Read in packages and SE function
```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
#Load all packages necessary for statistical anlaysis and figure production
library(ggplot2)
library(multcomp)
library(nlme)
library(grid)
library(Rmisc)
library(gridExtra)
library(emmeans)
library(cowplot)

```

#Load Data
```{r}
#Read in data files used in anlaysis 
#Pre vs Post Analysis
  #This data set contains all data for both the guided and autonomous formats (confidence, applicability, and perceptions of the CURE survey constructs)
  model=read.csv("Models.csv")
    #Relevel course iterations to display in order of semester implementation, Guided followed by Autonomous
    model$Experience=factor(model$Experience, levels=c("Guided", "Autonomous"))
    #Relevel time-point to display in order of course survey implementation (pre and the post-course survey timepoints)
    model$Time=factor(model$Time, levels=c("Pre", "Post"))

#Analysis between formats
  #Dowload data set with calculated gains (difference in pre- and post-course survey responses)
  gains=read.csv("Gains.data.csv")
    #Relevel Year to display in order of course iteractions (Guided in 2018 and Autonomous in 2019)
    gains$Year=factor(gains$Year, levels=c("Guided", "Autonomous"))
```

#Pre and Post-Course Survey Comparisons: Confidence Measures 
##Guided Format
```{r}
#Subset data set to include only measures of Confidence
conf=subset(model, Skill == "Confidence")
#Pre and post comparison in guided format
#Subset data to isolate responses from the guided format
conf.18=subset(conf, Experience == "Guided")
#Remove "Abiity to identify weaknesses" question, as it was only asked in the post-course survey
conf.18=subset(conf.18, Subskill != "Weakness")

#Run linear model to compare pre and post-course student reports of confidence
conf.18pp=lme(Score~as.factor(Time)*Subskill, random= ~1|ID, data=conf.18, na.action=na.omit)
#Summary output
anova(conf.18pp)

#Run emmeans for pairwise comparisons between pre and post-course responses for each survey question from the confidence construct in the guided format
confmeans18=emmeans(conf.18pp, list(pairwise ~ as.factor(Time)|Subskill), adjust = "tukey")
confmeans18

##Plot confidence survey measures based on estimated means pairwise comparisons and adjusted p-values
plot(confmeans18, by = "Subskill", comparisons = TRUE, horizontal = FALSE, color="darkgreen" )
#Explination of titles:
  #Design= I can design an experiment from beginning to end.
  #Notebook = I am confident in my ability to keep a well-structured lab notebook properly detailing experiments.
  #Peform = I can perform an experiment without aid, when given a protocol.
```

#Autonomous Format
```{r}
#Repeat all analyses for pre and post comparison in autonomous format
#Pre and post comparison in guided format
#Subset data to isolate responses from the guided format
conf.19=subset(conf, Experience == "Autonomous")
conf.19=subset(conf.19, Subskill != "Weakness")

#Run linear model to compare pre and post-course student reports of confidence
conf.19pp=lme(Score~as.factor(Time)*Subskill, random= ~1|ID, data=conf.19, na.action=na.omit)
#Summary output
anova(conf.19pp)

#Run emmeans for pairwise comparisons between pre and post-course responses for each survey question from the confidence construct in the guided format
confmeans19=emmeans(conf.19pp, list(pairwise ~ Time|Subskill), adjust = "tukey")
confmeans19

##Plot confidence survey measures based on estimated means pairwise comparisons and adjusted p-values
plot(confmeans19, by = "Subskill", comparisons = TRUE, horizontal = FALSE, color="darkgreen" )
#Explination of titles:
  #Design= I can design an experiment from beginning to end.
  #Notebook = I am confident in my ability to keep a well-structured lab notebook properly detailing experiments.
  #Peform = I can perform an experiment without aid, when given a protocol.
```

#Pre and Post-Course Survey Comparisons: Applicability Measures 
##Guided Format
```{r}
#Subset data to include only Applicability measures
app=subset(model, Skill == "Applicability")
#Pre and post comparison in guided format
#Subset data to isolate responses from the guided format
app.18=subset(app, Experience == "Guided")
#Remove "Abiity to identify weaknesses" question, as it was only asked in the post-course survey
app.18=subset(app.18, Subskill != "Weakness")

#run linear model to compare pre and post-course student reports of applicability
app.18pp=lme(Score~Time*Subskill, random= ~1|ID, data=app.18, na.action=na.omit)
#Summary report
anova(app.18pp)

#Run emmeans for pairwise comparisons between pre and post-course responses for each survey question from the applicability construct in the guided format
appmeans18=emmeans(app.18pp, list(pairwise ~ Time|Subskill), adjust = "tukey")
appmeans18
##Plot applicability survey measures based on estimated means pairwise comparisons and adjusted p-values
plot(appmeans18, by = "Subskill", comparisons = TRUE, horizontal = FALSE, color="darkgreen" )
#Explination of titles:
  #Discover= Research that I do in lab courses will lead to scientific discovery.
  #Everyday = The practices taught in molecular biology courses are applicable in everyday life.
  #Skills = In laboratory classes, I gain skills that will be applied in my future career.
```

##Autonomous Format
```{r}
#Repeat all analyses for pre and post comparison in autonomous format
#Pre and post comparison in autonomous
#Subset data to isolate responses from the autonomous format
app.19=subset(app, Experience == "Autonomous")

#run linear model to compare pre and post-course student reports of applicability
app.19pp=lme(Score~Time*Subskill, random= ~1|ID, data=app.19, na.action=na.omit)
#Summary report
anova(app.19pp)

#Run emmeans for pairwise comparisons between pre and post-course responses for each survey question from the applicability construct in the guided format
appmeans19=emmeans(app.19pp, list(pairwise ~ Time|Subskill), adjust = "tukey")
appmeans19

##Plot applicability survey measures based on estimated means pairwise comparisons and adjusted p-values
plot(appmeans19, by = "Subskill", comparisons = TRUE, horizontal = FALSE, color="darkgreen" ) 
#Explination of titles: 
  #Discover= Research that I do in lab courses will lead to scientific discovery.
  #Everyday = The practices taught in molecular biology courses are applicable in everyday life.
  #Skills = In laboratory classes, I gain skills that will be applied in my future career.
```

#Effect of Course Format on Student Perceptions: Measures of gains and post-course responses 
##Perspectives of the CURE Measures 
```{r}
#Subset data to include only measures of student perception of the CURE format
cure=subset(model, Skill == "CURE")

#Run linear model for student reported scores (based on Likert-Scale reports) between experiences (guided vs autonomous) by each subskill (survey question)
cure.lm=lm(Score~Experience*Subskill, data=cure, na.action=na.omit)
#Summary output
anova(cure.lm)
#Run emmeans for pairwise comparisons between guided and autonomous formats for each survey question from the CURE format construct
cure.means=emmeans(cure.lm, list(pairwise ~ Experience|Subskill), adjust = "tukey")
#Print results
cure.means

#Plot CURE format survey measures based on estimated means pairwise comparisons and adjusted p-values
plot(cure.means, by = "Subskill", comparisons = TRUE, horizontal = FALSE, color="darkgreen" )


#subset only significant comparisons for publication plot
cure.sub=subset(cure, Subskill == "Time"| Subskill == "Benefit"| Subskill == "Recommend" | Subskill == "In.engage" |Subskill == "Discovery")

#Sanity Check
#Run linear model for significant student reported scores (based on Likert-Scale reports) between experiences (guided vs autonomous) by each subskill (survey question)
curesub.lm=lm(Score~Experience*Subskill, data=cure.sub, na.action=na.omit)
anova(curesub.lm)
cure.sub.means=emmeans(curesub.lm, list(pairwise ~ Experience|Subskill), adjust = "tukey")
cure.sub.means

#Plot only significant relationships for publication figure 1
cure.plot=plot(cure.sub.means, by = "Subskill", comparisons = TRUE, horizontal = FALSE, color="darkgreen", xlab="Perceptions of the CURE" )+
  theme_bw() 
cure.plot

#Explination of titles: 
  #Benefit = I believe students benefit from a class taught in the CURE format.
  #Discovery = I participated in a project that will lead to scientific discovery.
  #In.engage = The CURE curriculum allowed instructors to become more engaged with students.
  #Recommend = I would to recommend this course to another student.
  #Time = The CURE required more time input than traditionally taught lab courses.
```

##Confidence Measures
```{r}
#Subset data to include only confidence measures
gains.con=subset(gains, Skill == "Confidence")

#Run linear model testing for differences in reported gains over the course of the semester between course formats
conf.gains.lm=(lme(Gains~Year*Subskill, data=gains.con, na.action=na.omit, random= ~1|Pre))

##Run emmeans for pairwise comparisons between guided and autonomous formats for each survey question from the confidence measures
conf.gains.means=emmeans(conf.gains.lm, list(pairwise ~ Year|Subskill), cov.keep="Year", adjust = "tukey")
conf.gains.means

##Plot emmeans adjust value gains by course format
conf.gains.plot=plot(conf.gains.means, by = "Subskill", comparisons = TRUE, horizontal = FALSE, color="darkgreen" ) +
  theme_bw()

#Explination of titles:
  #Design= I can design an experiment from beginning to end.
  #Notebook = I am confident in my ability to keep a well-structured lab notebook properly detailing experiments.
  #Peform = I can perform an experiment without aid, when given a protocol.
```

##Applicability Measures 
```{r}
#subset data to include only applicability measures
gains.app=subset(gains, Skill == "Applicability")

#Run linear model testing for differences in reported gains over the course of the semester between course formats
app.gains.lm=(lm(Gains~Year*Subskill, data=gains.app, na.action=na.omit, random= ~1|Pre))

##Run emmeans for pairwise comparisons between guided and autonomous formats for each survey question from the applicability measures
app.gains.means=emmeans(app.gains.lm, list(pairwise ~ Year|Subskill), cov.keep="Year", adjust = "tukey")
app.gains.means

##Plot emmeans adjust value gains by course format
app.gains.plot=plot(app.gains.means, by = "Subskill", comparisons = TRUE, horizontal = FALSE, color="darkgreen" ) +
  theme_bw()
#Explination of titles:
  #Discover= Research that I do in lab courses will lead to scientific discovery.
  #Everyday = The practices taught in molecular biology courses are applicable in everyday life.
  #Skills = In laboratory classes, I gain skills that will be applied in my future career.
```

#Draw multi panel plot of gains
```{r}
#Build multi-panel plot for figure 1 of publication 
p=ggdraw() +
  #Applicability comparisons between formats
  draw_plot(app.gains.plot, x = 0, y = 0.66, width = 0.6, height = .28) +
  #Confidence comparisons between formats
  draw_plot(conf.gains.plot, x = 0, y = .33, width = 0.6, height = .28)+
  #Perception of CURE between formats
  draw_plot(cure.plot, x = 0, y = 0.0, width = 1, height = 0.28) +
  #Add panel labels to plot
   draw_plot_label(label = c("C", "B","A"), size = 15,
                  x = c(0, 0 ,0), y = c(0.33, 0.66,0.99)) 
  
#Add white space margin to figure 
p5= p + theme(plot.margin=unit(c(15,15,15,15),"mm")) 

#Save as high quality png file
ggsave(p5, file="multipanel.gains.png", width=10, height=12, dpi=600)

p5
```

